intRo

### 2015-01-11 presentations/departmental-seminar/index.Rmd
New slides again

 - `R` is great, but requires students to have some knowledge/interest in programming
 - JMP is powerful, but too big
      - Licenses
      - Inconsistent UI
 - Want students to focus on data analysis rather than fight with software

@@

## Homework 1
 - *Data*: OECD PISA Results in Focus report to assess the workforce readiness of 15-year old students
 - *Goal*: Explore graphically and numerically how the students perceive academics and math
 - `intRo` *Tasks*:
      1. Make a summary of the Enjoy.Maths variable. What proportion of these students agree or strongly agree with the statement "I enjoy mathematics"?
      1. Make a barchart of the variable Enjoy.Maths.
      1. Give the conditional distribution of "Strongly agree'' given the Country.
      2. Obtain a contingency table and mosaic plot of the relationship between Country and Enjoy.Maths

>>>>

 - `R` is great, but requires students to have some knowledge/interest in programming
 - `JMP` is powerful, but too big
      - Licenses and inconsistent UI
 - New tools recently released to spark an interest in `R`
      - `Swirl` and DataCamp teach `R` programming
      - Project MOSAIC facilitates learning, but assumes knowledge of `R`
 - Want students to focus on data analysis rather than fight with software

@@

## Homework 1
 - *Data*: OECD PISA Results in Focus report to assess the workforce readiness of 15-year old students
 - *Goal*: Explore graphically and numerically how the students perceive academics and math
 - `intRo` *Tasks*:
      1. Make a barchart of the variable Enjoy.Maths.
      1. Make a summary of the Enjoy.Maths variable. What proportion of these students agree or strongly agree with the statement "I enjoy mathematics"?
      2. Obtain a contingency table and mosaic plot of the relationship between Country and Enjoy.Maths. Print contingency tables with the **Count** and **Column Proportion** values.
